\chapter{Introduction}
\label{chapter:intro}

This master's thesis purpose is to increase the understanding about limited liability housing companies' purchasing decision making in order to improve the service selling in a business to business to customer context. The study uses design science research approach and it is conducted as a service design project in a case company.

This chapter begins by presenting the background and motivation for the research and introducing the case company. Then the problem and research questions are presented and finally, the structure of the thesis is introduced.

\section{Background and Motivation}

In Finland about 2.7 million people are living in approximately 88 000 limited liability housing companies \parencite{REMF, Stats}. This limited liability housing company regime is an unique setting compared to other countries and it is dominant form of ownership in multi-apartment buildings in Finland \parencite{Lujanen:2017}. The operation of the limited liability company is regulated by the Finnish law \parencite{YIT}.

There are a lot of books and online material to support and guidance the people who are in the board of a limited liability housing company, referred later on also as a \emph{housing company}. In addition, it is discussed a lot that the work in a housing company can be a hassle and people do not want to participate in the operation of the housing company. However, there is a lack of knowledge and understanding about the purchase decision making process as well as the motivation of the people to be in the board.

This study tries to fill this knowledge gap by researching and understanding the people who are members of a housing company board and create a better way to reach the thousands of housing companies by identifying some similarities between them.

Related to the energy industry this study aims to facilitate a more customer-centric approach since according to \textcite{Fader:2012} energy firms do not refer to their customers as \emph{customers} but \emph{rate-payers}. This emphasizes how the energy firms view their customers and what could be changed, since according to \textcite{ByerPersonas:2015} basic rule of successful businesses is to know your customers.

\section{Introduction to Leanheat}

The case company in this study is Leanheat which provides a software solution that enables the space  heating optimization of centrally heated multi-family residential buildings. This is done by installing wireless sensors to track temperature and humidity, and a connection to the central heating controller is established. The system collects data from apartments, heating system and weather in order to automatically create a thermodynamic model for the building. Then the space heating is optimized based on the parameters resulting a minimized simultaneous usage of heat and thus lowering the peak loads caused by it. \parencite{LenheatArticle:2019}

The traditional heating system can not adjust to the changing weather or the thermodynamic properties of the building. In addition, the traditional system does not communicate with other systems inside the buildings nor with the buildings within the same network. This causes a suboptimal behaviour in the system, since it possible that all of these components require high heat power at the same time. \parencite{LenheatArticle:2019}

The benefits of the Leanheat's solution for district heating companies are that 1) the peak loads are 20 \% lower and primary return temperatures are two to four degrees lower, 2) heat production is optimized with demand forecasts and demand response and 3) data from the buildings offer new business models to be used and developed. For residents the solution provides stable and better indoor conditions. \parencite{LenheatArticle:2019}

In Finland, from the big apartment buildings around one third is owned by the professional property owners and in that specific market the case company is already the market lead. The rest of the buildings are housing companies which means that reaching them as clients is strategically important in order to grow bigger in the market.

Leanheat and district heating companies are forming partnerships because the system provides a way for the district heating companies to optimize their energy production. Moreover, based on the research done by \textcite{Energyindustry:2019} customers are becoming active in acquiring services which means that the energy companies should be more active in providing service business in order to engage better with their customers.

\section{Problem Statement}

As stated above, acquiring limited liability housing companies as clients is difficult, because there are tens of thousands of them and those are run by laypersons. In addition, people have tendency to favour the "status quo" -situation which means that the goal is to keep the situation as it is rather than developing it. In the context of living, the stabilised situation without any remarkable deficiencies leads to the situation where no changes are wished for. \parencite{AsoyKorjaustoiminta:2013}

Selling services for housing companies requires resources and knowledge about how they operate and the reasons for their actions. On top of that, district heating companies are valuable since currently they have their exiting customer relationships with housing companies because they provide them heat. The research will concentrate on creating new and better understanding on the purchase decision making processes inside housing companies by exploring the background motivation for people to be in the board and what affects the decision making. With this understanding it is then possible to design and develop a sales process guidance and guidelines on how to reach the potential market of the housing companies. Thus, the first research question is formed as follows:\\\\
\emph{RQ1: What affects the purchase decision making process in a limited liability housing companies?}\\

The results gained from the first research question are then utilized in order to find out how energy companies could sell their services more efficiently for the housing companies. By doing this research the aim is to provide new information and guidance for energy companies which would then increase sales as well as reduce lead times and customer acquisition costs. To answer this, the second research question is formulated as follows:\\\\
\emph{RQ2: How to improve current sales process with the knowledge of limited liability housing company's decision making process?}\\

\section{Structure of the Thesis}
\label{section:structure} 

In the next chapter, the background information about limited liability housing companies is studied and presented to gain understanding about what they are and how they operate. In addition, Chapter~\ref{chapter:background} provides information about he energy industry in Finland and an introduction of the science behind decision making. Lastly, Chapter 2 introduces the concept of customer centricity and service design. Then, in Chapter~\ref{chapter:methods} the research methods are presented along with the description on how the methods were implemented in the study. In Chapter~\ref{chapter:results} the results of the study are presented. Finally, the discussion related to the results of the study as well as limitations of the study and future research are discussed in the Chapter~\ref{chapter:discussion}.